From DSL to HPC Component Models

### 2015-07-23 WOLFHPC15/article/ms_msc.tex
wolfhpc15 23_07

\begin{figure}[h!]
\begin{lstlisting}[basicstyle=\small,mathescape,frame=single,language=C++]
program ::= "mesh:" meshid 
            "mesh domains:" listmeshdom
            "computation domains:" 
                       listcompdom
            "no intersections:"
                       listnointer
            "data:" listdata
            "time:" iteration
            "computations:" listcomp
listmeshdom ::= meshdom listmeshdom
             |  meshdom
listcompdom ::= compdom listcompdom
             |  compdom
compdom ::= compdomid "in" listmeshdom
listnointer ::= nointer listnointer
                  |  nointer
nointer ::= compdomid and compdomid
listdata ::= data listdata
          |  data
data ::= dataid "," meshdom
iteration ::= num
listcomp ::= comp listcomp
          |  comp
comp ::= dataid "=" compid "=({" 
            listdataid "}," compdomid 
            ["," neighborid] ")"
listdataid ::= dataid listdataid
            |  dataid
comptype ::= "stencil"
      |  "local"
      |  "bound"
\end{lstlisting}
\caption{Grammar of the MS language}
\label{fig:grammar}
\end{figure}

@@

\paragraph{Computation domains} A computation domain can be seen as a subpart of a meh domain which will be used during computation phase. For each computation domain is indicated the mesh domain identifier from which it is built. By default two computation domains always intersect except when precise in the section \emph{no intersections}. For example
\begin{lstlisting}[basicstyle=\small,mathescape,frame=single,language=C++]
computation domains:
  allcell in cell
  alledgex in edgex
  alledgey in edgey
  part1edgex in edgex
  part2edgex in edgex
no intersections:
  part1edgex and part2edgex
\end{lstlisting}
In this example, an entire computation domain is defined for each mesh domain, and additionnally two subpart of the mesh domain edgex are defined. It is then precised that part1edgex and part2edgex do not intersect.

>>>>

\begin{figure}[h!]
\begin{lstlisting}[basicstyle=\small,mathescape,frame=single,language=C++]
program ::= "mesh:" meshid 
            "mesh domains:" listmeshdom
            "computation domains:" 
                       listcompdom
            "independent:"
                       listinde
            "data:" listdata
            "time:" iteration
            "computations:" listcomp
listmeshdom ::= meshdom listmeshdom
             |  meshdom
listcompdom ::= compdom listcompdom
             |  compdom
compdom ::= compdomid "in" listmeshdom
listinde ::= inde listinde
          |  inde
inde ::= compdomid and compdomid
listdata ::= data listdata
          |  data
data ::= dataid "," meshdom
iteration ::= num
listcomp ::= comp listcomp
          |  comp
comp ::= dataid "=" compid "=({" 
            listdataid "}," compdomid 
            ["," neighborid] ")"
listdataid ::= dataid listdataid
            |  dataid
comptype ::= "stencil"
          |  "local"
          |  "bound"
\end{lstlisting}
\caption{Grammar of the MS language}
\label{fig:grammar}
\end{figure}

@@

\paragraph{Computation domains} A computation domain can be seen as a subpart of a meh domain which will be used during computation phase. For each computation domain is indicated the mesh domain identifier from which it is built. By default two computation domains always intersect except when precise in the section \emph{no intersections}. For example
\begin{lstlisting}[basicstyle=\small,mathescape,frame=single,language=C++]
computation domains:
  allcell in cell
  alledgex in edgex
  alledgey in edgey
  part1edgex in edgex
  part2edgex in edgex
independent:
  part1edgex and part2edgex
\end{lstlisting}
In this example, an entire computation domain is defined for each mesh domain, and additionnally two subpart of the mesh domain edgex are defined. It is then precised that part1edgex and part2edgex do not intersect.
